\centering DAOSYS: Smart DAO Protocol for Decentralized Finance

### 2022-09-23 latex/whitepaper/article.tex
update

To realize proper tokenomics design, from an engineering perspective, it is highly inefficient to invest resources into development without first conducting a proper simulations of the design to test specifications for various outcomes. This is what every DeFi project in the crypto space is not doing. This is why we are introducing an open source python package to simulate various sandboxed components of DAOSYS so that project engineers, managers and designers can pre-plan outcomes prior to investing valuable resources into development.

With this tool, DAOSYS designers can utilize the plug and play components of our simulator to build tokenomics mockups for business planning purposes so that teams can come together and get collective consensus alongside potential users and investors. Not only is this tool applicable to DAOSYS, it can be used as a general purpose tool to simulate DEX activity for anyone wishing to setup their own liquidity pool (LP) and wish to stress test their ideas prior to development. This can be used as a powerful design tool to explore the limitations of an DeFi project idea prior to committing valuable resources on development costs (ie, Devs and Project Managers). Table \ref{table:simulator_components} highlights the main components of the simulator, so that potential users of the system can get an idea of what to expect.

\begin{table}[h]
\centering
\begin{tabular}{ |l|l| } 
\hline
 \textbf{Simulator Component} & \textbf{Description} \\
\hline
Agents          & Entities that engage with the system, and are  \\
                & subcategorized into tokens and users \\
Events          & Agnostic events that take place within the \\ 
				& system (eg, mint, deposit, withdraw, swap, \\
				& and rebase) \\
ModelQueue      & Queue of univariate events that are modelled \\
				& aprior that can be fed into the system as \\
				& events\\
Actions         & Event actions that are fed into the system \\
				& performed by agents; they can either be single \\
				& stand-alone independent event actions or \\
				& chained together with dependency \\
ActionBatch     & Batches of actions chained together into a \\
				& sequence which can be repeated; there is only \\
				& one assigned time delta per batch, and there is \\
				& no limit as to the number of batches that can be \\
				& created \\
Liquidity Pools & Pool of two token agents managed by constant \\ 
				& product trading \\
Orchestrator    & Manages agents and actions working within the \\ 
				& system \\
Event Queue     & Queue of storable actions \\
Event Executor  & Final step which executes queue of action \\
				& events \\
\hline
\end{tabular}
\caption{Descriptions of DeFi python simulator components; refer to Fig. \ref{fig:simulator} to see how components interact with one another.}
\label{table:simulator_components}
\end{table}

We have a working beta version of the simulator which is available through Syscoin’s Github repository. This simulator is being built alongside DAOSYS, and we are using this to understand the ROI and design considerations for DAOSYS’s first usecase (ie, Masternode Yield Farming). Since the simulator is still in the beta stage, the setup is currently not realized to its full intention. However, a downloadable demo of this tool is ready for others in the community to begin using. For a mini python tutorial on how to use this tool, please refer to \cite{Moo22B} and refer to \cite{DAOSim22} for a series of example Jupyter notebooks.

@@

Prior to launch, we are waiting for Syscoin's L2 (ie, Rollux) \cite{ROL22, Sig21a, Sig21b} with Syscoin's Proof-of-Data Availability (PoDA) \cite{PODA22} to go into production. While it is technically possible that DAOSYS can run from any layer 1 (L1) EVM blockchain, it is our intention that it be launched when Rollux goes live. Currently, DAOSYS is running on the Rollux testnet where it is running a test implementation for Pegasys, which is Syscoin's premiere decentralized exchange (DEX).

We are expecting to launch DAOSYS in the in the early part of 2023 with crypto's first Masternode Yield Farm as its first functioning child DAO; see Fig. \ref{fig:daosys_launch}. Hence other projects running Masternodes will be incentivised to use our template and join the ecosystem to earn additional yield following the business case outlined in Section \ref{sec:yield_farming}.

\begin{figure}[h!]
\includegraphics[width=3in]{img/daosys_launch.png}
\caption{DAOSYS expected ecosystem at launch} 
\label{fig:daosys_launch}
\end{figure}

@@

@@

The Masternode Yield Farming tokenomics model has two main components: (a) Masternode rewards; and (b) DAOSYS rewards. From the a high-level perspective, users will commit the predetermined amount of liquidity to purchase a Masternode, the funds used for this purchase are staked thus used to generate $Coins_{New}$ in accordance to the specifications described in \cite{Sig21b}, which is as follows:

\begin{itemize}
\item \textbf{Block time:} 150 seconds
\item \textbf{Halving interval:} 210240 (1 year)
\item \textbf{Base Rewards:}  96.25 SYS per block deflated 5 percent every 210240 blocks
\item \textbf{NEVM Rewards:}  10.55 SYS per block (not deflated). EIP1559 model
\item \textbf{Governance Proposals:}  10 percent of Base Rewards paid out every 17520 blocks (1 month)
\item \textbf{Miner/Masternode Subsidy:}  90 percent of Base Rewards. 25 percent of this value goes to miner, 75 percent of this value goes to masternode
\item \textbf{Masternode Minimum Subsidy:} 5.275 SYS (can not go below this amount even accounting for deflation)
\item \textbf{Masternode collateral requirement:} 100,000 SYS
\item \textbf{Masternode seniority}: 35 percent increase after 210240 blocks (1 year), 100 percent increase after 525600 blocks (2.5 years)
\end{itemize}
Using the rule set described in the above specifications, we determine the Masternode rewards using the following relationship: 
\begin{equation*}
MN_{Rewards} = (Blocks_{Num}) (Coins_{New}) \left(\frac{Nodes_{Num}}{Supply_{New}}\right)
\end{equation*}
where current supply is calculated via the following:
\begin{equation*}
Supply_{New} = Supply_{Prev} + Coins_{New} - Fee_{TX} 
\end{equation*}
and $Fee_{TX}$ is calculated in accordance to Section \ref{appendix:tx_fee_burn}. Using Masternode returns, we calculated the USD value using Monte Carlo price projections as per Section \ref{appendix:monte_carlo}. Final total returns were determined via the following: 
\begin{equation*}
Total_{Rewards} = MN_{Rewards} + DAOSYS_{Rewards} 
\end{equation*}

@@

To model transaction fee burn to determine the supply end we used Ethereum fee data to serve as a proxy. We have determined that transaction fees follow an exponential growth that can be modelled via the following log-log model:
\begin{equation}
ln(\hat{y_{t}}) = a + bln(x_{t})
\end{equation}
where parameters $a$ and $b$ and its confidence intervals can be estimated using Ordinary Least Squares (OLS).

\subsection{Point Price Predictions: Monte Carlo}
\label{appendix:monte_carlo}
To generate point predictions for the price of Syscoin, we made some assumptions. This is where price was given the freedom to fluctuate between \$0.25 to \$25 USD / SYS over the 5-year projection interval (ie, 2023-2028) while maintaining an overall upward logarithmic growth (like most successful crypto projects typically do). To do this we generated a set up Monte Carlo point predictions using the following:

\begin{equation}
\label{eqn:trend}
	\mathbf{y}_{t} = c + \mathbf{\tilde{z}}_{t}e^{k z_{t}}
\end{equation}
where the random drift term $\mathbf{\tilde{z}}_{t}$ normalized between the interval [$a_{lwr}$,$a_{upr}$] given by:
\begin{equation}
\label{eqn:min_max}
	\mathbf{\tilde{z}}_{t}= \frac{\mathbf{z}_{t} - min(\mathbf{z}_{t})}{max(\mathbf{z}_{t}) - min(\mathbf{z}_{t})}
\end{equation}
and $\mathbf{z}_{t}$ is an ARIMA(1,1,1) process, given by:
\begin{equation}
\label{eqn:drift}
	\mathbf{z}_{t} = \gamma + \mathbf{z}_{t-1} + \phi_{1} \mathbf{z}_{t-1} - \phi_{1} \mathbf{z}_{t-2} +  \theta_{1} \mathbf{e}_{r-1} + \mathbf{e}_{t}
\end{equation}
where $\phi_{1}$ is the AR(1) coefficient, $\theta_{1}$ is the MA(1) coeffcient, and $\mathbf{e}_{t} \sim N(0, \sigma^2)$. Once these sets were generated, we estimated the 5$^{th}$ and 95$^{th}$ percentiles to attain the 90\% prediction interval. To see a table of these predictions, along with the lower and upper bounds, please refer to \cite{Moo22A}.

>>>>

To realize proper tokenomics design, it is highly inefficient to invest resources into development without first conducting a proper simulations of the design to test specifications for various outcomes. This is what every DeFi project in the crypto space is not doing. This is why we are introducing an open source python package to simulate various sandboxed DeFi components of DAOSYS so that project engineers, managers and designers can pre-plan outcomes prior to investing valuable resources into development.

With this tool, DAOSYS designers can utilize the plug and play components of our simulator to build tokenomics mockups for business planning purposes so that teams can come together and get collective consensus alongside potential users and investors. Not only is this tool applicable to DAOSYS, it can be used as a general purpose tool to simulate DEX activity for anyone wishing to setup their own liquidity pool (LP) and wish to stress test their ideas prior to development. This can be used as a powerful design tool to explore the limitations of an DeFi project idea prior to committing valuable resources on development costs (ie, Devs and Project Managers). Table \ref{table:simulator_components} highlights the main components of the simulator, so that potential users of the system can get a higher level understanding of how the simulator package functions.

\begin{table}[h]
\centering
\begin{tabular}{ |l|l| } 
\hline
 \textbf{Simulator Component} & \textbf{Description} \\
\hline
Agents          & Entities that engage with the system, and are  \\
                & subcategorized into tokens and users \\
Events          & Agnostic events that take place within the \\ 
				& system (eg, mint, deposit, withdraw, swap, \\
				& and rebase) \\
ModelQueue      & Queue of univariate events that are modelled \\
				& aprior that can be fed into the system as \\
				& events\\
Actions         & Event actions that are fed into the system \\
				& performed by agents; they can either be single \\
				& stand-alone independent event actions or \\
				& chained together with dependency \\
ActionChains    & Actions that have dependencies on other \\
				& actions as inputs \\				
ActionBatch     & Batches of actions placed together into a \\
				& repeatable sequence; there is only one \\
				& assigned time delta per the pass of each batch, \\
				& and there is no limit as to the number of \\
				& batches that can be created \\
Liquidity Pools & Pool of two token agents managed by constant \\ 
				& product trading \\
Orchestrator    & Manages agents and actions working within the \\ 
				& system \\
Event Queue     & Queue of storable actions \\
Event Executor  & Final step which executes queue of action \\
				& events \\
\hline
\end{tabular}
\caption{Descriptions of DeFi python simulator components; refer to Fig. \ref{fig:simulator} to see how components interact with one another.}
\label{table:simulator_components}
\end{table}

We have a working beta version of the simulator which is available through Syscoin’s Github repository. This simulator is being built alongside DAOSYS, and we are using this to understand the ROI and design considerations for DAOSYS’s first usecase (ie, Masternode Yield Farming). Since the simulator is still in the beta stage, the setup is currently not realized to its full intention. However, a downloadable demo of this tool is available from Syscoin's Github repository for the community to begin using. For a mini python tutorial on how to use this tool, please refer to \cite{Moo22B} and refer to \cite{DAOSim22} for a series of example Jupyter notebooks.

@@

Prior to mainnnet release, Syscoin's L2 (ie, Rollux) \cite{ROL22, Sig21a, Sig21b} must launch first along with Syscoin's Proof-of-Data Availability (PoDA) \cite{PODA22}. While it is technically possible that DAOSYS can run from any layer 1 (L1) EVM blockchain, it is our intention that it be launched when Rollux goes live. Currently, DAOSYS is running on the Rollux testnet where it is also running a test DAO for Pegasys, which is Syscoin's premiere decentralized exchange (DEX).

We are expecting to launch DAOSYS in the early part of 2023 with crypto's first Masternode Yield Farm as its first functioning child DAO; see Fig. \ref{fig:daosys_launch}. Hence other projects running Masternodes will be incentivised to use our template and join the ecosystem to earn additional yield following the business case outlined in Section \ref{sec:yield_farming}.

\begin{figure}[h!]
\includegraphics[width=3in]{img/daosys_launch.png}
\caption{DAOSYS expected ecosystem at launch in early 2023} 
\label{fig:daosys_launch}
\end{figure}

@@

DAOSYS allows for the self-sovereign capital coordination within decentralized organizations, which is the main problem that this project addresses. It does this via its new ASE technology which is made possible through an extension of the multi-facet proxy (ie, Diamonds) outlined in EIP-2535. We call this extension the Hyper-diamond standard.

DAOSYS is planning to launch on Rollux's mainnet in the early part of 2023, which is Syscoin's L2. During this event, we are also planning to launch the first of a new class of DAOs called Masternode Yield Farming. In this discussion, we have presented five-year ROI estimates using our DeFi python simulator that can also be used by community members who may be interested in testing out various business cases for DAO DeFi strategies.

@@

The Masternode Yield Farming tokenomics model has two main components: (a) Masternode rewards; and (b) DAOSYS rewards. To aquire Masternode rewards, users stake liquidity to purchase a Masternode, thus used to generate $Coins_{New}$ in accordance to the specifications described in \cite{Sig21b}, which are as follows:

\begin{itemize}
\item \textbf{Block time:} 150 seconds
\item \textbf{Halving interval:} 210240 (1 year)
\item \textbf{Base Rewards:}  96.25 SYS per block deflated 5 percent every 210240 blocks
\item \textbf{NEVM Rewards:}  10.55 SYS per block (not deflated). EIP1559 model
\item \textbf{Governance Proposals:}  10 percent of Base Rewards paid out every 17520 blocks (1 month)
\item \textbf{Miner/Masternode Subsidy:}  90 percent of Base Rewards. 25 percent of this value goes to miner, 75 percent of this value goes to masternode
\item \textbf{Masternode Minimum Subsidy:} 5.275 SYS (can not go below this amount even accounting for deflation)
\item \textbf{Masternode collateral requirement:} 100,000 SYS
\item \textbf{Masternode seniority}: 35 percent increase after 210240 blocks (1 year), 100 percent increase after 525600 blocks (2.5 years)
\end{itemize}
Using the rule set described above, we determine Masternode rewards via the following: 
\begin{equation*}
MN_{Rewards} = (Blocks_{Num}) (Coins_{New}) \left(\frac{Nodes_{Num}}{Supply_{Cur}}\right),
\end{equation*}
where current supply is calculated via the following:
\begin{equation*}
Supply_{Cur} = Supply_{Prev} + Coins_{New} - Fee_{TXBurn},
\end{equation*}
and $Fee_{TXBurn}$ is calculated in accordance to Section \ref{appendix:tx_fee_burn}. Finally, total rewards were determined via the following: 
\begin{equation*}
Total_{Rewards} = MN_{Rewards} + DAOSYS_{Rewards}. 
\end{equation*}
To estimate $DAOSYS_{Rewards}$, we used our DeFi python simulator; for tutorials and example templates one can reference \cite{Moo22B}. To estimate returns in USD, we applied the Monte Carlo procedure to estimate future point predictions for the USD value of Syscoin, as per Section \ref{appendix:monte_carlo}.

@@

To model transaction fee burn to determine the supply end we used Ethereum fee data to serve as a proxy. We have determined that transaction fees follow an exponential growth that can be modelled via the following log-log model:
\begin{equation}
ln(\hat{y_{t}}) = a + bln(x_{t}),
\end{equation}
where parameters $a$ and $b$ and its confidence intervals can be estimated using Ordinary Least Squares (OLS).

\subsection{Point Price Predictions: Monte Carlo}
\label{appendix:monte_carlo}
To generate point predictions for the price of Syscoin, we made some assumptions. Price was given the freedom to fluctuate between \$0.25 to \$25 USD / SYS over the 5-year projection interval (ie, 2023-2028) while maintaining an overall upward logarithmic growth, which is a price behavior characteristic that can be attributed to most successful crypto projects. To do this we generated a set of Monte Carlo point predictions, $\mathbf{\hat{p}}_{t}$, using the following:

\begin{equation}
\label{eqn:trend}
	\mathbf{\hat{p}}_{t} = c + \mathbf{\tilde{z}}_{t}e^{k z_{t}},
\end{equation}
where random drift term $\mathbf{\tilde{z}}_{t}$ is normalized between the interval [$a_{lwr}$,$a_{upr}$] as given by:
\begin{equation}
\label{eqn:min_max}
	\mathbf{\tilde{z}}_{t}= \frac{\mathbf{z}_{t} - min(\mathbf{z}_{t})}{max(\mathbf{z}_{t}) - min(\mathbf{z}_{t})},
\end{equation}
and $\mathbf{z}_{t}$ is an ARIMA(1,1,1) process, given by:
\begin{equation}
\label{eqn:drift}
	\mathbf{z}_{t} = \gamma + \mathbf{z}_{t-1} + \phi_{1} \mathbf{z}_{t-1} - \phi_{1} \mathbf{z}_{t-2} +  \theta_{1} \mathbf{e}_{r-1} + \mathbf{e}_{t},
\end{equation}
where $\phi_{1}$ is the AR(1) coefficient, $\theta_{1}$ is the MA(1) coeffcient, and $\mathbf{e}_{t} \sim N(0, \sigma^2)$. Once these sets were generated, we estimated the 5$^{th}$ and 95$^{th}$ percentiles to attain the 90\% prediction interval. Refer to \cite{Moo22A} for a table of these point predictions, along with its corresponding confidence interval.
